Environmental stress drives intermediate plant and pollinator specialisation

### 2020-03-09 paper/manuscript.Rmd
Title page to conform to EL requirements

<!-- **Running title:** XX -->

<!-- **Type of article:** XX -->

<!-- **Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text. -->

<!-- **Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes. -->

<!-- **Number of references:** `r n_references + nrow(interaction_citations)` -->

@@

<!-- **Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. We will include the DOI here. -->

<!-- **Author contributions:** XX -->

>>>>

**Running title:** Environmental stress drives specialisation.

**Type of article:** Letter.

**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.

**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.

**Number of references:** `r n_references + nrow(interaction_citations)`

@@

**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. We will include the DOI here.

**Author contributions:** EFC conceived the study. EFC and AL compiled cleaned the data. EFC analysed the data. All authors contributed to the writing of the manuscript and study design.
